Total_SC

### 2020-05-21 doc/totalSC.Rmd
DEBUGGED and CLEANED up the setup rmd and MS_v2 scripts

```{r setup, echo=FALSE, warning=FALSE, include = FALSE}
library(ggplot2)
library(plyr)
library(dplyr)
#load main MLH1 files to merge MLH1 cell data with the sc data 
setwd("~./")

@@

#these data generated by running "python script --, it should be re-run when new cells are added to the anon.csv file
SC.skel = read.csv("~./MLH1repo/data/SCskel_output_nov19.csv", header = TRUE, strip.white = TRUE)

#load BivData  
load(file="~./MLH1repo/data/CleanBivData_6.3.20.RData")
#load(file="C:/Users/alpeterson7/Documents/MLH1repo/data/CleanBivData_13.2.20.RData")

#Curated list

#strain specific xlsx sheets (why?)

# Total.SC
# input: output from RW SC_skel run over Anon_Data images. The file names are random
# output: DFs of merged MLH1 and Skel data, cell and mouse levels
```

# Goals

Why include these results in the Main MLH1 results?

 - test if **greater SC area in females is a conserved trait of heterochiasmy**

 - test how average total SC correlates / contributes to mean CO

## Discribe these Data

output from RW SC_skel run over Anon_Data images. The file names are random

The Main dataframe is the Merge MLH1 + skel data.

## Running the Python Script

@@

### ToDo

- How will I test these / and adjust for XX?

- Look up the python output

- Check for outliers in the skel data

- rerun the Python script

- check that the mice from mixed models are in these

ToDo re-run the pipeline, to get measues for SKIVE and MOLF females
molf has almost eq SC -- but this is just 1 female

@@

```{r clean.data, echo=FALSE, warning=FALSE}
#format all factors to numbers
SC.skel$bin_size  <- as.character(SC.skel$bin_size )
SC.skel$skel_size  <- as.character(SC.skel$skel_size)

@@

#check for duplicatations of the random name
original_DF$Random.Name <- as.character(original_DF$Random.Name)
duplies <- original_DF[duplicated(original_DF$Random.Name),]
#3 duplicate rows in original DF -- because Random name was blank -- how will these be matched to total.SC?
```

```{r merge.DF, echo=FALSE}

#MERGEING MLH! with SKEL
MLH1.merge.Skel <- merge(original_DF, SC.skel, by.x = "Random.Name", by.y = "rand_name", all= F)
OG.MLH1.merge.Skel <- MLH1.merge.Skel #raw version of DF

@@

```{r grab.nice.mice.setup, echo=FALSE, warning=FALSE}
#https://rcompanion.org/handbook/G_03.html
#testing random effects within lme
#notes for testing random effects

#variance is still chr
AP_mouse_table_w.Ages$var <- as.numeric(AP_mouse_table_w.Ages$var)

#use the merged DF to filter by age 
AP_mouse_table_w.Ages$strain <- AP_mouse_table_w.Ages$strain.x
AP_mouse_table_w.Ages$sex <- AP_mouse_table_w.Ages$sex.x
AP_mouse_table_w.Ages$subsp <- AP_mouse_table_w.Ages$subsp.x
#main file, make everything unordered factors
AP_mouse_table_w.Ages <- add_species(AP_mouse_table_w.Ages)

DF.HetC.MixedModel <- AP_mouse_table_w.Ages[AP_mouse_table_w.Ages$species == "M.musculus",]

DF.HetC.MixedModel <- subset(DF.HetC.MixedModel, select= -c(sex.x, sex.y,
                            subsp.y,subsp.x,
                    category.y, category.x,
                        strain.x,strain.y, mouse.1  )  )

#REMOVE EXTRA STRAINS
DF.HetC.MixedModel <- DF.HetC.MixedModel[DF.HetC.MixedModel$subsp != "Cast",]
#remove musc strains
DF.HetC.MixedModel <- DF.HetC.MixedModel[DF.HetC.MixedModel$strain != "AST",]
DF.HetC.MixedModel <- DF.HetC.MixedModel[DF.HetC.MixedModel$strain != "TOM",]
#remove PERC, MOLF, CZECH, (no females)
DF.HetC.MixedModel <- DF.HetC.MixedModel[DF.HetC.MixedModel$strain != "CZECH",]
DF.HetC.MixedModel <- DF.HetC.MixedModel[DF.HetC.MixedModel$strain != "PERC",]

DF.HetC.MixedModel <- droplevels(DF.HetC.MixedModel)#remove levels not used

#mean_co.HQ  (this might remove some of the MOLF males)
DF.HetC.MixedModel.HQ <- DF.HetC.MixedModel[DF.HetC.MixedModel$Ncells > 9,]
#DF.HetC.MixedModel.HQ <- DF.HetC.MixedModel.HQ[DF.HetC.MixedModel.HQ$age.weeks < 25,]
#above should only apply to males

DF.HetC.MixedModel.HQ <- DF.HetC.MixedModel.HQ[!(is.na(DF.HetC.MixedModel.HQ$mouse)|DF.HetC.MixedModel.HQ$mouse==""),]

@@

```{r check.lists, echo=FALSE}
#MLH1.merge.Skel
#OG.MLH1.merge.Skel

@@

library(tidyr)

@@

```{r more.blahs, echo=FALSE}
#WSB -- WSB_curation, WSB_female output on big External
#not sure why Curated bivData catching more categories than this above

#this table now has merged bin/skel, and have been curated (but it doesn't have data on the curated bivalents)
#the curated list is the current bottle neck

#I should start inventory  how many mice are in each curated category

Skel.summary.table <- ddply(.data=skel.mice_from.MM.list, 
                 .(category),
                 summarize, 
                 ncells = length(unique(Original.Name)),
                 nmice = length(unique(mouse)),
                 mean.MLH1 = mean(adj_nMLH1.foci, na.rm = TRUE),
                 var.MLH1 = var(adj_nMLH1.foci, na.rm = TRUE),

```{r cleaning.up, echo=FALSE}
#clean up this DataFrame REMOVE 'X'
MLH1.merge.Skel <- MLH1.merge.Skel[ !grepl("X", MLH1.merge.Skel$Batch) , ]
MLH1.merge.Skel <- MLH1.merge.Skel[ !grepl("x", MLH1.merge.Skel$X) , ]
MLH1.merge.Skel <- MLH1.merge.Skel[!(is.na(MLH1.merge.Skel$quality) | MLH1.merge.Skel$quality==""), ]

@@

#it seems like this has duplicates
MLH1.merge.Skel.DUPs <- MLH1.merge.Skel[duplicated(MLH1.merge.Skel$Random.Name),]
#with new dataframe, there are 0 duplicates..
#make sure to seperate mice based on adult and juvinille

#remove for now
#MLH1.merge.Skel <- MLH1.merge.Skel %>% distinct()

@@

@@

#Below threshold is are the values to use

#write.xlsx2(MLH1.merge.Skel, "Total.SC_merge.MLH1.xlsx", sheetName = "Sheet1", 
#            col.names = TRUE, row.names = FALSE, append = FALSE)
```

@@

```{r ploting, echo=FALSE}
Total.SC.box <- ggplot(data = MLH1.merge.Skel, aes(y=skel_size, x=strain, color=sex) ) + geom_boxplot()+ggtitle("Total SC Measures")

@@

```{r crop.stuff, echo=FALSE}

@@

table of clean crop stat
table of total (minus clean crop, stat)
 difference in means is the amount of error

for some categories the difference is ~20% between the means
usuall difference means the croped version has less compared to other

```{r more.plot, echo=FALSE}

@@

```{r table.making, echo=FALSE}
#mouse level
mouse.level.skel <- ddply(.data=MLH1.merge.Skel,
                          .(mouse),
                          summarize, 
                          ncells = length(unique(Original.Name)),
                          nmice = length(unique(mouse)),
                          mean.MLH1 = mean(nMLH1.foci, na.rm = TRUE),
                          mean.skel = mean(skel_size),
                          mean.bin = mean(bin_size)
)

@@

```{r mouse.level.plot, echo=FALSE, warning=FALSE}

>>>>

```{r setup, echo=FALSE, warning=FALSE, include = FALSE}
library(ggplot2)
library(plyr)
library(dplyr)
library(tidyr)
library(xlsx)

#load main MLH1 files to merge MLH1 cell data with the sc data 
setwd("~./")

@@

# Total.SC
# input: output from RW SC_skel run over Anon_Data images. The file names are random
# output: DFs of merged MLH1 and Skel data, cell and mouse levels

#these data generated by running "python script --, it should be re-run when new cells are added to the anon.csv file
#SC.skel = read.csv("~./MLH1repo/data/SCskel_output_nov19.csv", header = TRUE, strip.white = TRUE)

#SC.skel = read.csv("~./MLH1repo/data/SCskel_output_feb20.csv", header = TRUE, strip.white = TRUE)

Total.SC_DF = read.xlsx2("~./MLH1repo/data/Total.SC_merge.MLH1.xlsx", header=TRUE, 1)

#this most recent version -- is missing most measures for MOLF_m
```

Read in most recent output, remove the outliers (by strain), WRITE out the excel file for the nice clean total sc file, output from RW SC_skel run over Anon_Data images. The file names are random  The Main dataframe is the Merge MLH1 + skel data.

## Running the Python Script Notes

@@

@@

# Clean Skel data

```{r clean.skel.data, echo=FALSE, warning=FALSE}

#format all factors to numbers
SC.skel$bin_size  <- as.character(SC.skel$bin_size )
SC.skel$skel_size  <- as.character(SC.skel$skel_size)

@@

#check for duplicatations of the random name
original_DF$Random.Name <- as.character(original_DF$Random.Name)
duplies <- original_DF[duplicated(original_DF$Random.Name),]
#3 duplicate rows in original DF -- because Random name was blank -- how will these be matched to total.SC?

@@

```{r merge.MLH1.skel, echo=FALSE}

#MERGEING MLH1 with SKEL by Random.Name
MLH1.merge.Skel <- merge(original_DF, SC.skel, by.x = "Random.Name", by.y = "rand_name", all= F)
OG.MLH1.merge.Skel <- MLH1.merge.Skel #raw version of DF

#no filename in the skel output
#MLH1.merge.Skel.FF <- merge(original_DF, SC.skel, by.x = "fileName", by.y = "fileName", all= F)
#OG.MLH1.merge.Skel <- MLH1.merge.Skel #raw version of DF

@@

#clean total.DF

Warning most of the number levels are factors, so to chanage to numbers -- they need to follow the order, factor -> chr -> number.

str(Total.SC_DF)#quality is a factor. must go factor - chr - number

```{r clean.total.DF, echo=FALSE}

#this is a nice merged excel file, still has X, and might have some 'outlier' images
Total.SC_DF.og <- Total.SC_DF
#quality is mess up here

Total.SC_DF$quality <- as.character(Total.SC_DF$quality)
Total.SC_DF$X <- as.character(Total.SC_DF$X)

#Total.SC_DF <- Total.SC_DF %>% filter(X != "X")
#remvove Xs
Total.SC_DF <- Total.SC_DF[ !grepl("X", Total.SC_DF$X) , ]
#Total.SC_DF$X <- droplevels(Total.SC_DF$X)

str(Total.SC_DF)
#check that there are only numbers in the quality
table(Total.SC_DF$quality)

#jj <- Total.SC_DF[ grepl("X", Total.SC_DF$X) , ]

#factor -> chr
Total.SC_DF$n <- as.character(Total.SC_DF$n)
Total.SC_DF$nMLH1.foci<- as.character(Total.SC_DF$nMLH1.foci)

Total.SC_DF$skel_size<- as.character(Total.SC_DF$skel_size)
Total.SC_DF$bin_size<- as.character(Total.SC_DF$bin_size)

#chr -> num
Total.SC_DF$quality<- as.numeric(Total.SC_DF$quality)
Total.SC_DF$n <- as.numeric(Total.SC_DF$n)
Total.SC_DF$nMLH1.foci<- as.numeric(Total.SC_DF$nMLH1.foci)

Total.SC_DF$skel_size<- as.numeric(Total.SC_DF$skel_size)
Total.SC_DF$bin_size<- as.numeric(Total.SC_DF$bin_size)

#table(Total.SC_DF$quality)

Total.SC has fewer cells than MLH1.merge (maybe the outliers have been removed). MLH1.merge has 'X'.

```{r check.DFs, echo=FALSE, eval=FALSE}

#compare the total.SC_DF

#MLH1.merge.Skel
#OG.MLH1.merge.Skel

@@

@@

```{r cleaning.up.MLH1.merge, echo=FALSE, eval=FALSE}

#clean up this DataFrame REMOVE 'X'
MLH1.merge.Skel <- MLH1.merge.Skel[ !grepl("X", MLH1.merge.Skel$Batch) , ]
MLH1.merge.Skel <- MLH1.merge.Skel[ !grepl("x", MLH1.merge.Skel$X) , ]
MLH1.merge.Skel <- MLH1.merge.Skel[ !grepl("X", MLH1.merge.Skel$X) , ]
MLH1.merge.Skel <- MLH1.merge.Skel[!(is.na(MLH1.merge.Skel$quality) | MLH1.merge.Skel$quality==""), ]

@@

@@

# Check Duplicates

```{r Duplicates, echo=FALSE, eval=FALSE}

Total.SC_DF_DUP.list <- Total.SC_DF[duplicated(Total.SC_DF$Random.Name),]
Total.SC_DF_DUP.list <- Total.SC_DF[duplicated(Total.SC_DF$fileName),]
#no Duplicates in total.SC

MLH1.merge.Skel_DUP.list <- MLH1.merge.Skel[duplicated(MLH1.merge.Skel$Random.Name),]
MLH1.merge.Skel_DUP.list <- MLH1.merge.Skel[duplicated(MLH1.merge.Skel$fileName),]

kk <- MLH1.merge.Skel$fileName[duplicated(MLH1.merge.Skel$fileName)]
```

total.SC doesn't have duplicates

# Remove Outliers

below are the list of cell images which have been removed because they look like outliers compared to other cells from that mouse.

Total.SC_DF  vs  MLH1.merge.Skel,  I think these both have outliers.

```{r totSC.viz4outliers, echo=FALSE}

# -- EXAMINE the ggplot scatter plots for outliers
#tot.sc <- ggplot(data= MLH1.merge.Skel, aes(y = bin_size, x=strain))+ #geom_jitter()+facet_wrap(~category, scales = "free")

#round 1
SC.skel.outliers_round1 <- c(
  #MLH1.merge.Skel  %>% filter(category == "WSB male") %>% filter(skel_size > 2000)
  "10apr15_31mar15_WSB_m3_sp1_4_rev.tif",

  #MLH1.merge.Skel  %>% filter(category == "WSB female") %>% filter(skel_size > 2700)       
            "17nov16_3nov15_WSB_f1_sp3_4_rev.tif","1may16_3nov15_WSB_f1_sp2_6_rev.tif",

    #MLH1.merge.Skel  %>% filter(category == "G male") %>% filter(skel_size > 20000) 
                      "19oct15_12oct15_G_m1_sp1_17.1_rev.tif",

  #MLH1.merge.Skel  %>% filter(category == "G female") %>% filter(skel_size > 20000) 
              "1mar16_20feb16_G_f3_sp1_8_rev.tif","21nov16_16jan16_G_f2_sp1_15_rev.tif",

  #MLH1.merge.Skel  %>% filter(category == "LEW male") %>% filter(skel_size < 1000)          
          "6mar18_1feb18_LEW_m1_sp1_21.5_rev",

  #MLH1.merge.Skel  %>% filter(category == "LEW female") %>% filter(skel_size > 20000)   
          "12jan17_4jan17_LEW_f1_sp1_32_rev.tif","20mar17_13jan17_LEW_f2_sp1_12_rev.tif","9apr18_1feb18_LEW_f1_sp1_23_rev.tif","9apr18_1feb18_LEW_f1_sp1_12_rev.tif",

       #MLH1.merge.Skel  %>% filter(category == "PWD male") %>% filter(skel_size > 20000)  
                      "6mar15_1mar15_PWD_m1_sp4_6.1_rev.tif","7mar15_1mar15_PWD_m1_sp4_2_rev.tif","20jul15_18may15_PWD_m2_sp1_10.2_rev.tif",

   #MLH1.merge.Skel  %>% filter(category == "PWD female") %>% filter(skel_size > 20000)
   "6may15_17apr15_PWD_f1_sp1_7_rev",

      #MLH1.merge.Skel  %>% filter(category == "KAZ male") %>% filter(skel_size < 1000)
            "6aug19_10jul19_KAZ_m1_sp1_7.1_rev.tif",

    # MLH1.merge.Skel  %>% filter(category == "KAZ female") %>% filter(skel_size > 30000)     
    "16feb18_1feb18_KAZ_f4_sp1_20_rev.tif",  "8feb18_1feb18_KAZ_f1_sp1_24_rev.tif",  
  "16feb18_1feb18_KAZ_f4_sp1_1_rev.tif",   "8feb18_1feb18_KAZ_f1_sp1_5_rev.tif",   
 "16feb18_1feb18_KAZ_f4_sp1_17_rev.tif",  "1mar18_1feb18_KAZ_f3_sp1_8_rev.tif",   
 "7feb18_11jan18_KAZ_f3_sp1_27_rev.tif",  "20apr18_11jan18_KAZ_f1_sp1_6_rev.tif", 
 "16feb18_1feb18_KAZ_f2_sp1_5.2_rev.tif", "16feb18_1feb18_KAZ_f2_sp1_15_rev.tif", 
"7feb18_11jan18_KAZ_f3_sp1_13_rev.tif",  "13apr18_1feb18_KAZ_f6_sp1_25_rev.tif" ,

  # MLH1.merge.Skel  %>% filter(category == "SKIVE female") %>% filter(skel_size > 10000)
    "10jun19_31may19_SKIVE_f6_sp1_47_rev.tif","10jun19_31may19_SKIVE_f6_sp1_7_rev.tif",

# MLH1.merge.Skel  %>% filter(category == "MOLF male") %>% filter(skel_size < 1200)
"4jun19_28sep18_MOLF_m1_sp1_10.1_rev.tif",

#MLH1.merge.Skel  %>% filter(category == "AST male") %>% filter(skel_size > 2100)
"16aug19_27aug18_AST_m1_sp1_23_rev.tif",

#MLH1.merge.Skel  %>% filter(category == "MSM female") %>% filter(skel_size > 20000)
"21nov17_16nov17_MSM_f3_sp1_24_rev.tif","21nov17_16nov17_MSM_f3_sp1_3_rev.tif", "21nov17_16nov17_MSM_f3_sp1_27_rev.tif","4dec17_16nov17_MSM_f2_sp1_10_rev.tif",
"5aug17_14jul17_MSM_f1_sp1_25_rev.tif","24jan18_31dec17_MSM_f3_sp1_3_rev.tif", 
"24jan18_31dec17_MSM_f3_sp1_22_rev.tif","21nov17_16nov17_MSM_f3_sp1_17_rev.tif",

#tt <- MLH1.merge.Skel  %>% filter(category == "SPIC female") %>% filter(skel_size > 20000)
"27dec17_4dec17_SPIC_f1_sp1_12_rev.tif",  "5apr18_31dec17_SPIC_f2_sp1_1_rev.tif",
 "26sep18_30may18_SPIC_f4_sp1_14_rev.tif", "4feb18_31dec17_SPIC_f1_sp1_21_rev.tif", 
 "5apr18_31dec17_SPIC_f2_sp1_22_rev.tif",  "27dec17_4dec17_SPIC_f1_sp1_40_rev.tif", 
 "4jul18_30may18_SPIC_f1_sp1_6_rev.tif",   "26sep18_30may18_SPIC_f4_sp1_6_rev.tif", 
 "29dec17_4dec17_SPIC_f2_sp1_10_rev.tif",  "5sep17_21aug17_SPI_f2_sp1_37_rev.tif" , 
 "5sep17_21aug17_SPI_f2_sp1_15_rev.tif",   "26sep18_30may18_SPIC_f4_sp1_24_rev.tif",
"29dec17_4dec17_SPIC_f2_sp1_16_rev.tif",  "5sep17_21aug17_SPI_f2_sp1_30_rev.tif",  
"4feb18_31dec17_SPIC_f1_sp1_5_rev.tif",   "5apr18_31dec17_SPIC_f2_sp1_25_rev.tif", 
 "26sep18_30may18_SPIC_f4_sp1_4_rev.tif",  "5sep17_21aug17_SPI_f2_sp1_22_rev.tif",  
 "5sep17_21aug17_SPI_f2_sp1_19_rev.tif",   "5sep17_21aug17_SPI_f2_sp1_29_rev.tif",  
 "26sep18_30may18_SPIC_f4_sp1_3_rev.tif",  "5sep17_21aug17_SPI_f2_sp1_5.2_rev.tif", 
 "29dec17_4dec17_SPIC_f2_sp1_6_rev.tif",   "13oct17_21aug17_SPI_f1_sp1_13_rev.tif"  )

MLH1.merge.Skel <- MLH1.merge.Skel[!MLH1.merge.Skel$fileName %in% SC.skel.outliers_round1, ]#62 removed

remove.mice_round2 <- c(
    #MLH1.merge.Skel  %>% filter(category == "G male") %>% filter(skel_size > 2500)
    "28jul15_22jun15_G_m2_sp1_5_rev.tif","12may15_30sep14_G_m5_sp1_26_rev.tif",

    #MLH1.merge.Skel  %>% filter(category == "G female") %>% filter(skel_size > 20000)
  "19oct15_12oct15_G_m1_sp1_17.1_rev.tif",

#MLH1.merge.Skel_2  %>% filter(category == "PWD male") %>% filter(skel_size > 2100)
"20jul15_18may15_PWD_m1_sp1_10_rev.tif","22mar15_10mar15_PWD_m2_sp1_11.2_rev.tif","22mar15_10mar15_PWD_m1_sp1_4.1_rev.tif","20jul15_18may15_PWD_m1_sp1_7.2_rev.tif",

#MLH1.merge.Skel_2  %>% filter(category == "PWD female") %>% filter(skel_size > 20000)
  "6may15_17apr15_PWD_f1_sp1_7_rev.tif",

  #MLH1.merge.Skel_2  %>% filter(category == "KAZ female") %>% filter(skel_size < 1000)
  "8feb18_1feb18_KAZ_f1_sp1_19_rev.tif",

#MLH1.merge.Skel_2  %>% filter(category == "LEW male") %>% filter(skel_size < 1000 | skel_size > 1750)
"6mar18_1feb18_LEW_m1_sp1_10_rev.tif","3mar15_13jan17_LEW_m1_sp1_15_rev.tif", "4feb17_4jan17_LEW_m1_sp1_13_rev.tif","6mar18_1feb18_LEW_m1_sp1_21.5_rev.tif",

#MLH1.merge.Skel_2  %>% filter(category == "LEW female") %>% filter(skel_size > 2750 ) 
"20mar17_13jan17_LEW_f2_sp1_10_rev.tif",

# MLH1.merge.Skel_2  %>% filter(category == "CAROLI male") %>% filter(skel_size < 1400 )
"31aug18_1mar18_CAROLI_m1_sp3_29.2_rev.tif",

#MLH1.merge.Skel_2  %>% filter(category == "MSM male") %>% filter(skel_size < 1200 )
"16aug17_5jul17_MSM_m1_sp1_6.1_rev.tif",

#tt <- MLH1.merge.Skel_2  %>% filter(category == "MSM female") %>% filter(skel_size > 2850 ) 
"29nov17_16nov17_MSM_f1_sp1_10_rev.tif", "4dec17_16nov17_MSM_f2_sp1_24_rev.tif", "21nov17_16nov17_MSM_f3_sp1_26_rev.tif",
#SPIC male  x
#SPIC female  x
#TOM x
#AST x
#CZECH male x

#MLH1.merge.Skel_2  %>% filter(category == "SPRET male") %>% filter(skel_size < 1900 ) 
 "24may17_8may17_SPRET_m1_sp1_21.1_rev.tif",
#SPRET female X
#MLH1.merge.Skel_2  %>% filter(category == "HMI male") %>% filter(skel_size < 1000 ) 
"29dec17_4dec17_HMI_m1_sp1_4.1_rev.tif"
)
#3remove.mice_round2

MLH1.merge.Skel <- MLH1.merge.Skel[!MLH1.merge.Skel$fileName %in% remove.mice_round2, ]

#MLH1.merge.Skel <- MLH1.merge.Skel[! (MLH1.merge.Skel$fileName %in% SC.skel.outliers_round1),]
#MLH1.merge.Skel <- MLH1.merge.Skel[! (MLH1.merge.Skel$fileName %in% remove.mice_round2),]
all.remove <- paste( c(SC.skel.outliers_round1, remove.mice_round2 ) )

Total.SC_DF <- Total.SC_DF[!Total.SC_DF$fileName %in% SC.skel.outliers_round1, ]
Total.SC_DF <- Total.SC_DF[!Total.SC_DF$fileName %in% remove.mice_round2, ]
#sum( length(SC.skel.outliers_round1), length(remove.mice_round2) )
```

`r sum( length(SC.skel.outliers_round1), length(remove.mice_round2) )` images were removed as probable outliers.  ~20 outliers were removed from total.sc.skel.

```{r category.table, echo=FALSE, eval=FALSE}

#I should start inventory  how many mice are in each curated category
Skel.summary.table <- ddply(.data=skel.mice_from.MM.list, 
                 .(category),
                 summarize, 
                 ncells = length(unique(Original.Name)),
                 nmice = length(unique(mouse)),
                 mean.MLH1 = mean(adj_nMLH1.foci, na.rm = TRUE),
                 var.MLH1 = var(adj_nMLH1.foci, na.rm = TRUE),

@@

#Below threshold is are the values to use
write.xlsx2(Total.SC_DF, "Total.SC_DF.xlsx", sheetName = "Sheet1", 
            col.names = TRUE, row.names = FALSE, append = FALSE)

#merge skel has more observations (are they dups?)
#write.xlsx2(MLH1.merge.Skel, "Merge.MLH1.xlsx", sheetName = "Sheet1", 
#            col.names = TRUE, row.names = FALSE, append = FALSE)
```

@@

```{r ploting, echo=FALSE, eval=FALSE}
Total.SC.box <- ggplot(data = MLH1.merge.Skel, aes(y=skel_size, x=strain, color=sex) ) + geom_boxplot()+ggtitle("Total SC Measures")

@@

```{r crop.stuff, echo=FALSE, eval=FALSE}

@@

table of clean crop stat, table of total (minus clean crop, stat, difference in means is the amount of error

For some categories the difference is ~20% between the means
.. usuall difference means the croped version has less compared to other.

```{r more.plot, echo=FALSE, eval=FALSE}

@@

```{r table.making, echo=FALSE, eval=FALSE}
#mouse level
mouse.level.skel <- ddply(.data=MLH1.merge.Skel,
                          .(mouse),
                          summarize, 
                          ncells = length(unique(Original.Name)),
                          nmice = length(unique(mouse)),
                          mean.MLH1 = mean(nMLH1.foci, na.rm = TRUE),
                          mean.skel = mean(skel_size),
                          mean.bin = mean(bin_size)
)

@@

```{r mouse.level.plot, echo=FALSE, warning=FALSE, eval=FALSE}
